\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/iteration1.tex
read for grammar

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}). Each of them has a number as ID and a letter representing the name. We recruited 14 participants from our institution for this study. 13 had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust, and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.

@@

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, list selection was perceived to be cumbersome. One user noted benefit of {\em IR selection} being \studyquote{more direct [than list mode]}, allowing users to focus on the targeted objects instead of the screen. One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}, and many participants compared the overall time of target acquisition. One subject pointed out that \studyquote{{\em IR selection} doesn't requires you to swipe a lot of times like list mode}.

>>>>

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}). Each of them has a number as ID and a letter representing the name. We recruited 14 participants from our institution for this study. 13 had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.

@@

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, IR selection was perceived to be more direct and pleasurable. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}, and many participants compared the overall time of target acquisition.
